Optimal (Multiway) Spatial Joins

### 2024-05-30 msj.tex

>>>>

It remains to show that we will not map two distinct rectangle $r_1^*, r_2^*\in \bigcup_{i = 1}^{k-2}R_i^*$ to the same tuple $\bm{t}\in \J(R_1',...,R_{k-2}')$. Suppose to the contrary that $r_1^*, r_2^*$ are mapped to the same tuple $\bm{t}$. Let $r_1^*, r_2^*$ be the top-sliced rectangles of $r_1'$ and $r_2'$ respectively. Since $r_1^*$ and $r_2^*$ are disinct, $r_1'$ is not the same as $r_2'$. By our mapping, $\gbot(B_{\bm{t}})$ is $r_1'$ and $r_2'$. Since $\gbot(B_{\bm{t}})$ is unique for each tuple $\bm{t}$, we have a contradiction. Therefore, each rectangle $r^*\in \bigcup_{i = 1}^{k-2}R_i^*$ is mapped to a unique tuple $\bm{t}\in \J(R_1',...,R_{k-2}')$.
